Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-23 bbbq_article.tex
Incorrect: Geert enjoyed 'Use of protein data in phylogenetics', fix https://github.com/richelbilderbeek/bbbq_article/issues/112

\paragraph{Does MHC-I present TMH-derived epitopes from pathogens as often?}

@@

\paragraph{MHC-II is expected to present TMHs}

@@

\paragraph{Does MHC-II present TMH-derived epitopes from pathogens as often?}

@@

\paragraph{Selection undetectable in whole proteome}

@@

\paragraph{Immunodominance}

The effective number of epitopes, however,
is much lower than the actual number of possible
epitopes, due to immunodominance. 
Immunodominance is a feature of the immune system,
due to which some epitopes dominate in causing an immune response,
where other (called subdominant) epitopes end up having no 
effect (\cite{akram2012immunodominance}).
The same study mentions 20 factors that influence the strength
of an immune response.
The most relevant factor for this study is the effect of
a mutation within an epitope, 
such as the in vitro example described in (\cite{berkhoff2004mutation}),
where one single mutation resulted in a 5-20\% weaker
response of virus-specific CD8+ T cells \richel{Fun experiment:
do this in silico}.
Due to immunodominance, we dare assume that there can be selection
for immune system avoidance, as the effective number of loci may be
low and effects of a single mutation noticeable.

@@

When using DNA sequences, one can use a skewed rate 
in non- versus synonymous mutation
to detect the signature of selection (\cite{murrell2015gene}).
Using AA sequences, however, has its advantages,
as its is closer to the actual phenotype
selection acts upon: DNA may never be translated to RNA,
or its RNA may never be transcribed (\cite{diz2012proteomics})
\richel{improve upon this point}.
When using a proteome in phylogenetic research,
we know that the majority of proteins are selected to just 
maintain their function most of the time, where
is the time spans there is selection, only a few AAs
can actually increase the 'fitness' of the 
protein (\cite{anisimova2009investigating}).
There, when generalizing the dynamics of mostly purifying selection (to maintain
a protein's function) and a short duration of positive selection,
those genes that are selected cannot be detected (\cite{yang2000statistical}).

>>>>

% \paragraph{Does MHC-I present TMH-derived epitopes from pathogens as often?}

@@

% \paragraph{MHC-II is expected to present TMHs}

@@

% \paragraph{Does MHC-II present TMH-derived epitopes from pathogens as often?}

@@

% \paragraph{Selection undetectable in whole proteome}

@@

@@

When using DNA sequences, one can use a skewed rate
in non- versus synonymous mutation
to detect the signature of selection (\cite{murrell2015gene}).
Using AA sequences, however, has its advantages,
as its is closer to the actual phenotype
selection acts upon: DNA may never be transcribed to RNA,
or its RNA may never be translated (\cite{diz2012proteomics})
\richel{improve upon this point}.
When using a proteome in phylogenetic research,
we know that the majority of proteins are selected to just
maintain their function most of the time, where
is the time spans there is selection, only a few AAs
can actually increase the 'fitness' of the
protein (\cite{anisimova2009investigating}).
There, when generalizing the dynamics of mostly purifying selection (to maintain
a protein's function) and a short duration of positive selection,
those genes that are selected cannot be detected (\cite{yang2000statistical}).
